### 2022-09-21 dissertation/chapters/09-conclusion.tex
✨ (review): Adding data and analysis

All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-287321.

>>>>

All data, source code, logs, configurations, scripts and analysis is hosted at: \url{https://github.com/arneschreuder/masters.ai} with raw empirical data made available on Google Cloud project id: masters-363209.
